Automated Program Verification and Synthesis of Embedded \& Cyber-Physical Systems: Advances and Challenges

### 2018-02-23 paper.tex
added section about IC3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Due to that limitation, BMC tools are typically susceptible to exhaustion of time or memory limits, when checking complex circuit-implementations or programs with loops, whose bounds are too large or cannot be statically determined. Indeed, such an issue has pushed researchers to overcome the depth limitation and propose extensions capable of proving global correctness.

%--------------------------------------
\subsection{Completeness}
\label{completeness}
%--------------------------------------

\textcolor{blue}{BMC can be used to find property violations up to the bound $k$ but not to prove properties, unless an upper bound is known on the depth of the state space, which is not generally the case. For software verification and synhtesis, we can adopt two different strategies in order to \emph{prove} properties: \textit{(i)} compute the \textit{completeness threshold}, which can be smaller than or equal to the maximum number of loop-iterations occurring in the program or \textit{(ii)} determine the high-level worst-case execution time (WCET), which also gives a bound on the maximum number of loop-iterations~\cite{handbook09,ckso04,Ganai08}. However, in practice, complex software systems involve large data-paths and complex expressions. Therefore, the verification conditions that arise from BMC of programs become harder to solve and require substantial amounts of memory to build.}

%--------------------------------------
\subsubsection{Induction-based Verification of C Programs}
%--------------------------------------

@@

%------------------------------------------------------
\subsubsection{Craig Interpolation}
\label{sec:CraigInterpolationInModelChecking}
%------------------------------------------------------

>>>>

Due to that limitation, BMC tools are typically susceptible to exhaustion of time or memory limits, when checking complex circuit-implementations or programs with loops, whose bounds are too large or cannot be statically determined. Indeed, such an issue has pushed researchers to overcome the depth limitation and propose extensions capable of proving global correctness. \textcolor{blue}{In particular, we can adopt two possible strategies to prove properties using BMC: \textit{(i)} compute the \textit{completeness threshold}, which can be smaller than or equal to the maximum number of loop-iterations occurring in the program or \textit{(ii)} determine the high-level worst-case execution time (WCET), which also gives a bound on the maximum number of loop-iterations~\cite{handbook09,ckso04,Ganai08}. However, in practice, complex software systems involve large data-paths and complex expressions. Therefore, the verification conditions that arise from BMC of programs become harder to solve and require substantial amounts of memory to build.}

%--------------------------------------
\subsection{Induction-based Verification of C Programs}
%--------------------------------------

@@

%--------------------------------------
\subsection{Property-based Reachability (or IC3)}
%--------------------------------------

\textcolor{blue}{The application of the \textit{k}-induction method is gaining popularity in the software verification community. Bradley {\it et al.} introduced  ``property-based reachability'' (or IC$3$) procedure for the safety verification of systems~\cite{Bradley12,Bradley13}; the authors have shown that IC$3$ can scale on certain benchmarks, where \textit{k}-induction fails to succeed.}

%------------------------------------------------------
\subsection{Craig Interpolation}
\label{sec:CraigInterpolationInModelChecking}
%------------------------------------------------------
